\chapter{Procedures and Deadlines}
\label{app:procedures}

\paragraph{Deadlines}
At least one semester prior to the semester in which you believe you will
complete all requirements for your degree, please be sure to consult with your
department's graduate administrative assistant or coordinator to be sure you
are aware of all requirements and deadlines with regards to your thesis and the
submission of your thesis.  Deadlines are printed in the course listings
schedule book and are posted online.  If you cannot make certain deadlines, you
may have to postpone your graduation accordingly.  M.S.\ and D.Sc.\ students
have a special deadline by which they must submit an initial draft of their
thesis so that it can be reviewed for formatting, to make sure it conforms to
the essential formatting requirements, as illustrated in this sample guide.
Ph.D.\ students must follow the requirements of the Office of Graduate Students
in Arts and Sciences (GSAS).  The GSAS office does not have an special
formatting deadlines, but you should still contact that office if you have
questions about your formatting.

\paragraph{Oral Examination}
Each member of the oral examining committee must be given a copy of the thesis
or dissertation, in final form, in sufficient time to study it before the oral
examination.  Members of the examining committee have the right to request
rescheduling of the examination if these copies are not made available to them
at least one week in advance of the scheduled examination date.  Copier paper
may be used for these preliminary copies.

\paragraph{Final Copies}
After the oral defense, final copies of the thesis or dissertation approved by
the examination committee and department are to be distributed as follows, on
or before the date stated in the current academic calendar.  All final copies
must be printed using only one side on high-quality (either watermarked or
specifying as having 10-25\% cotton), 8.5 x 11 inch white paper, and minimum
20-pound weight.  Students should submit their final materials to the office(s)
listed in the first item below, plus all other materials itemized below should
be submitted accordingly, if needed:
\begin{itemize}
  \item \uline{Four copies of the thesis or dissertation need to be submitted
	  as follows:} Each should be placed in a separate manila envelope with
	  a copy of the title page securely attached.  One of these two will be
	  retained in the Washington University library; another will be sent
	  back to you after being professionally bound;  the other two copies
	  are for your advisor and department.  Two copies (along with the
	  following listed materials) get delivered to Engineering Student
	  Services.  Two copies get delivered to your department (also with the
	  short title page included as listed immediately below---although,
	  none of the other additional items listed further below are needed
	  for the department copies).  \textbf{NOTE FOR PH.D.\ STUDENTS:}  All
	  four copies get delivered to the GSAS Office.  See GSAS dissertation
	  guidelines from their web site.
        
  \item \uline{a loose sheet containing} (1) a \uline{short title} of 35
	  letters or less (including spaces), (2) the author's last name, (3)
	  the degree, and (4) the year of its award, centered on the page and
	  punctuated as in the example.\footnote{See the sample short title
	  page for this document} This short title sheet is to be placed at end
	  of your thesis/dissertation.
	
  \item one \uline{extra} loose copy of the abstract (this applies to doctoral
	  students only), \uline{double spaced}, for publication in
	  Dissertation Abstracts. 
  
  \item one \uline{extra} loose copy of the \uline{title page} (this applies to
	  doctoral students only) for the microfilming contract.

  \item the \uline{original \textbf{and} a photocopy of the University
	  Microfilms Inc.\ publishing agree\-ment contract} (this applies to
	  doctoral students only).  This contract is available from the
	  Engineering Student Services web site.  If a registration to your
	  claim to copyright is desired, attach a certified check, cashier's
	  check, or money order for the current price listed in the University
	  Microfilms contract.  Personal checks are not accepted.  The
	  microfilming contracts are available in Lopata 324.  The check or
	  money order should not have an expiration date.
\end{itemize}

Four copies in all are to be submitted, as per details listed above.  See the
first bulleted item for full details.  Please follow instructions carefully.
Contact Engineering Student Services if you have questions.  Ph.D.\ students
may contact the Graduate School of Arts and Sciences.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "thesis-main"
%%% End: 
